Distributed Tic Tac Toe:\\ Peer-to-Peer Team-Based Gaming System

### 2017-12-01 paper/paper.tex
Added one more reference

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/DAS-topology.png}
	\caption{Topology for Distributed Tic Tac Toe}
	\label{fig:topology1}
\end{figure}

@@

% TODO: reference for state design pattern
The \texttt{Role} interface allows the application to differentiate between \texttt{Leader} and \texttt{Player} classes which extend it. It utilises the State design pattern to allow players to seamlessly have their role changed when required (eg. if the current leader disconnects).

@@

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/DAS-topology-election.png}
	\caption{Proposed Topology for UDP-based Version of System} % TODO: is this caption out of date?
	\label{fig:topology-election}
\end{figure}

>>>>

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/DAS-topology.png}
	\caption{Topology for Distributed Tic-Tac-Toe}
	\label{fig:topology1}
\end{figure}

@@

% TODO: reference for state design pattern
The \texttt{Role} interface allows the application to differentiate
between \texttt{Leader} and \texttt{Player} classes which extend
it. It utilises the State design pattern
\cite{DBLP:books/daglib/0078642} to allow players to seamlessly have
their role changed when required (eg. if the current leader
disconnects).

@@

\begin{figure}[h]
	\includegraphics[width=\linewidth]{images/DAS-topology-election.png}
	\caption{Topology changes after a leader disconnects}
	\label{fig:topology-election}
\end{figure}
